---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# VisCollin

<!-- badges: start -->
[![License](https://img.shields.io/badge/license-GPL%20%28%3E=%202%29-brightgreen.svg?style=flat)](https://www.gnu.org/licenses/gpl-2.0.html) 
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Last Commit](https://img.shields.io/github/last-commit/friendly/VisCollin)](https://github.com/friendly/VisCollin)
<!-- badges: end -->

The `VisCollin` package provides
methods to calculate diagnostics for multicollinearity among predictors in a linear or
generalized linear model. Also provides methods to visualize those diagnostics following Friendly & Kwan (2009),
"Where’s Waldo: Visualizing Collinearity Diagnostics", _The American Statistician_, **63**, 56–65.

These include:

* better tabular presentation of collinearity diagnostics that highlight the important numbers.
* a semi-graphic tableplot of the diagnostics and 
* a collinearity biplot of the _smallest dimensions_ of predictor space, where collinearity is most apparent.

## Installation

You can install the development version of VisCollin from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("friendly/VisCollin")
```

## Example

This example uses the `cars` data set.
```{r cars}
library(VisCollin)
library(car)

data(cars)
str(cars)
```

Fit model
```{r cars-mod}
cars.mod <- lm (mpg ~ cylinder + engine + horse + weight + accel + year, 
                data=cars)
Anova(cars.mod)
```

Check the VIFs

```{r}
vif(cars.mod)
```

Diagnostics

```{r}
cd <- colldiag(cars.mod, 
               add.intercept=FALSE, center=TRUE)

print(cd, fuzz = 0.3)
```


## References

Belsley, D.A.,  Kuh, E.  and Welsch, R. (1980).
_Regression Diagnostics_, New York: John Wiley & Sons.

Belsley, D.A. (1991).
_Conditioning diagnostics, collinearity and weak data in regression_.
New York: John Wiley & Sons.

Friendly, M., & Kwan, E. (2009).
"Where’s Waldo: Visualizing Collinearity Diagnostics." _The American Statistician_, **63**, 56–65.

