---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# VisCollin

<!-- badges: start -->
[![License](https://img.shields.io/badge/license-GPL%20%28%3E=%202%29-brightgreen.svg?style=flat)](https://www.gnu.org/licenses/gpl-2.0.html) 
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Last Commit](https://img.shields.io/github/last-commit/friendly/VisCollin)](https://github.com/friendly/VisCollin)
<!-- badges: end -->

The `VisCollin` package provides
methods to calculate diagnostics for multicollinearity among predictors in a linear or
  generalized linear model. Also provides methods to visualize those diagnostics following Friendly & Kwan (2009),
  "Where’s Waldo: Visualizing Collinearity Diagnostics", The American Statistician, 63, 56–65.
  These include a semi-graphic tableplot of the diagnostics and a collinearity biplot of the smallest dimensions
  of predictor space, where collinearity is most apparent.

## Installation

You can install the development version of VisCollin from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("friendly/VisCollin")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(VisCollin)
## basic example code
```


## References

Belsley, D.A.,  Kuh, E.  and Welsch, R. (1980).
_Regression Diagnostics_, New York: John Wiley & Sons.

Belsley, D.A. (1991).
_Conditioning diagnostics, collinearity and weak data in regression_.
New York: John Wiley & Sons.

Friendly, M., & Kwan, E. (2009).
"Where’s Waldo: Visualizing Collinearity Diagnostics." _The American Statistician_, **63**, 56–65.

